\documentclass[a4paper,12pt]{article}
\usepackage{./../TLCresume}



\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line

%====================
% EXPERIENCE
%====================

\subsection{Machine Learning Engineer \hfill Jan 2024}
\subtext{ExSeed Health, Contract\hfill remote}
\vspace*{1pt}
Field: Machine Learning \& Computer Vision \\
\vspace*{\spaceAfterField}
\begin{zitemize}
\item Developing segmentation and tracking algorithms in Pytorch and YOLOv8. 
\item Using DevOps, MLOps methodology.
\item Deploying the system in AWS (SageMaker, Lambda, DynamoDB and S3).
\item Result: Improved tracking of sperm cells, automatic analysis of sperm quality.
\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{Data Scientist \hfill Aug 2023 - Dec 2023}
\subtext{Meddoc Flow ApS., Contract \hfill remote}
\vspace*{1pt}
Field: Natural Language Processing \\
\vspace*{\spaceAfterField}
\begin{zitemize}
\item Developed RAG and NLP algorithms to retrieve Medical Device Regualtion (MDR) queries in a vector database.
\item Using LlamaIndex and Truera to create a RAG pipeline and implement the triad metrics: context relevance, groundedness and answer relevance; and retrieval algorithms: sentence window retrieval, auto-merging retrieval.
\item Result: Proof of Concept retrieval system to query the MDR with NLP.
\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{PhD student \hfill Sep 2021 - Jan 2024}
\subtext{Department of Clinical Medicine, Aarhus University \hfill Aarhus, Denmark}
\vspace*{1pt}
Field: Machine Learning \& Hypertension \\
\vspace*{\spaceAfterField}
\begin{zitemize}
\item New time-series contrast analysis of laser speckle images. Improved optical system.
\item Result: 2 publications, patent.
\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{Machine Learning internship \hfill Jul 2019 - Sep 2019}
\subtext{Telef\'onica Alpha, Health Moonshot \hfill Barcelona, Spain}
\vspace*{1pt}
Field: Machine Learning \& Human Computer Interaction \\
\vspace*{\spaceAfterField}
\begin{zitemize}
\item EDA and time-series analysis of phone sensors, electrodermal activity from empatica's wristband and self reported questionnaires in a phone app.
\item Result: Insights into the relation between sensor data, arousal state and self-reported states of happiness.
\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{Marie Curie Early Stage Researcher \hfill Mar 2017 - Apr 2020}
\subtext{Department of Computing Science, University of Glasgow \hfill Glasgow, Scotland}
\vspace*{1pt}
Field: Machine Learning, Human-Computer Interaction \& Attachment Theory
\vspace*{\spaceAfterField}
\begin{zitemize}
\item EDA and mapping of electrodermal activity to vibrotactile cues and psychophysics.
\item Result: Insight into the use of vibrotactile feedback to represent arousal in emotionally shut down people.
\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\vspace*{5pt}
\subsection{Biomedical Engineer \hfill Mar 2015 - Apr 2017}
\subtext{Max-Plank Institute for Metabolism Research \hfill Cologne, Germany}
\vspace*{1pt}
Field: MRI \& fMRI analysis
\vspace*{\spaceAfterField}
\begin{zitemize}
\item Designed Experiment. Segmented brainstem in MRI images, analyzed fMRI data. Used time-series analysis to debug the processing pipeline.
\item Result: Successful completion of an ambitious project.
\end{zitemize}



%====================
% EXPERIENCE
%====================

\subsection{Machine Learning Research Fellowship \hfill Mar 2013 - Apr 2014}
\subtext{Department of Mathematics, University of Barcelona \hfill Barcelona, Spain}
\vspace*{1pt}
Field: Machine Learning \& Atherosclerosis
\vspace*{\spaceAfterField}
\begin{zitemize}
\item Implemented new metrics and alignment algorithms on Intravascular Ultrasound images.
\item Result: Faster and more reliable alignment of IVUS sequences from coronary arteries.
\end{zitemize}

\end{document}


% ----------------
% END of DOCUMENT
% ----------------

\end{document}
