\documentclass[a4paper,12pt]{article}
\usepackage{./../TLCresume}



\begin{document}

%using zitemize instead of itemize will allow for tighter spacing before and after each line

%====================
% EXPERIENCE
%====================

\subsection{Machine Learning Engineer \hfill Jan 2024}
\subtext{ExSeed Health, Contract\hfill remote}
\vspace*{1pt}
Field: Machine Learning \& Computer Vision \\
\vspace*{\spaceAfterField}
\begin{zitemize}

    \item Improved tracking of sperm cells, automatic analysis of sperm quality.
    \item Developing segmentation and tracking algorithms in Pytorch and YOLOv8. 
    \item Using DevOps, MLOps methodology.
    \item Deploying the system in AWS (SageMaker, Lambda, DynamoDB and S3).

\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{Data Scientist \hfill Aug 2023 - Dec 2023}
\subtext{Meddoc Flow ApS., Contract \hfill remote}
\vspace*{1pt}
Field: Natural Language Processing \\
\vspace*{\spaceAfterField}
\begin{zitemize}
    \item Proof of Concept retrieval system to query the MDR with NLP.
    \item Developed RAG and NLP algorithms to retrieve Medical Device Regualtion (MDR) queries in a vector database.
    \item Using LlamaIndex and Truera to create a RAG pipeline and implement the triad metrics: context relevance, groundedness and answer relevance; and retrieval algorithms: sentence window retrieval, auto-merging retrieval.

\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{PhD student \hfill Sep 2021 - Jan 2024}
\subtext{Department of Clinical Medicine, Aarhus University \hfill Aarhus, Denmark}
\vspace*{1pt}
Field: Machine Learning \& Hypertension \\
\vspace*{\spaceAfterField}
\begin{zitemize}
\item Publication of a new analysis method for laser speckle images using statistical modelling. 
\item Publication of improved optical system for laser speckle imaging.
\item Patent co-inventor.
\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{Marie Curie Early Stage Researcher \hfill Mar 2017 - Apr 2020}
\subtext{Department of Computing Science, University of Glasgow \hfill Glasgow, Scotland}
\vspace*{1pt}
Field: Machine Learning, Human-Computer Interaction \& Attachment Theory
\vspace*{\spaceAfterField}
\begin{zitemize}
    \item Insight into the use of vibrotactile feedback to represent arousal in emotionally shut down people.
    \item EDA and mapping of electrodermal activity to vibrotactile cues and psychophysics.

\end{zitemize}
\vspace*{5pt}

%====================
% EXPERIENCE
%====================

\subsection{Machine Learning internship \hfill Jul 2019 - Sep 2019}
\subtext{Telef\'onica Alpha, Health Moonshot \hfill Barcelona, Spain}
\vspace*{1pt}
Field: Machine Learning \& Human Computer Interaction \\
\vspace*{\spaceAfterField}
\begin{zitemize}
    \item Insights into the relationship between sensor data, arousal state and self-reported states of happiness.
    \item Exploratory data analysis and time-series analysis of phone sensors, electrodermal activity from empatica's wristband and self reported questionnaires in a phone app.

\end{zitemize}
\vspace*{5pt}


%====================
% EXPERIENCE
%====================

\vspace*{5pt}
\subsection{Biomedical Engineer \hfill Mar 2015 - Apr 2017}
\subtext{Max-Plank Institute for Metabolism Research \hfill Cologne, Germany}
\vspace*{1pt}
Field: MRI \& fMRI analysis
\vspace*{\spaceAfterField}
\begin{zitemize}
    \item Carried out the design, execution and analysis of an MRI and fMRI study.
    \item Segmented brainstem in MRI images, analyzed fMRI data. Used time-series analysis to debug the processing pipeline.

\end{zitemize}



%====================
% EXPERIENCE
%====================

\subsection{Machine Learning Research Fellowship \hfill Mar 2013 - Apr 2014}
\subtext{Department of Mathematics, University of Barcelona \hfill Barcelona, Spain}
\vspace*{1pt}
Field: Machine Learning \& Atherosclerosis
\vspace*{\spaceAfterField}
\begin{zitemize}
    \item Faster and more reliable alignment of IVUS sequences from coronary arteries.
    \item Implemented new metrics and alignment algorithms on Intravascular Ultrasound images.

\end{zitemize}

\end{document}


% ----------------
% END of DOCUMENT
% ----------------

\end{document}
